Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection\thanks{This research is supported by the Natural Science Foundation of China (Grant No. 61572043), and the National Key Research and Development Program (Grant No. 2016YFB1000704).}

### 2017-03-22 paper/acmFormat.tex
remove duplicate references

\documentclass{sig-alternate-05-2015}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{bm}

@@

\maketitle
\begin{abstract}
In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
For humanbeing, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumalation of happened things. 
In \textsc{NSDetector}, 1) balanced for effectiveness and efficiency, normal states are trained as topical words and their frequencies; 2) historical topical word frequencies are initialized from knowledge base with chi-squared test; 3) topical word frequencies on targeted corpus are maintened by KB-Prior-LDA, using the normal states in knowledge base as prior; 4) events are detected by monitoring the change of topical word frequencies. 
Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
And further experiments on \textit{reddit} and \textit{arXiv} also demonstrate that \textsc{NSDetector} can be easily adapted on other cyberspace datasets.
%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well. 
\end{abstract}

@@

\textbf{Event.} We define the event in the given time window \(t\) as the set of tweets denoted by \( \{ \bm{w_{te}}\}\).
The event related tweets in set \( \{ \bm{w_{te}}\}\)  hold two properties: (1) it is different from user \(u\)'s long term interests and (2) it is similar with other tweets in the set.
The task of event detection is to find out all the events in corpus.
Different methods treat the above properties in different ways: LSH based methods\cite{petrovic2010streaming} treat the difference and simliarity in word vector space; while the topic model based methods\cite{timeUserLDA2012finding} take the semantic meaning into consideration.
Under the framework of topic model, we divide the topics into user interest related topics and bursty event related topics, and further promote an online learning model UMIETM.
\subsection{Normal States' Initialization}
%TODO
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{img/normalStatesFromHistoryInfo.pdf}  
    \caption{Illustration on how to train normal states from wikipedia,( an approximation to the full history information).}
    \label{fig:modelDesc}
\end{figure}

>>>>

\documentclass{sig-alternate-05-2015}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
%\usepackage{algorithm}
\usepackage{bm}

@@

\maketitle
\begin{abstract}
In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
For human being, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things. 
%TODO
In \textsc{NSDetector}, 1) balanced for effectiveness and efficiency, normal states are trained as topical words and their chi-squared scores, and initialized by knowledge base; 2) topical word frequencies on targeted corpus within the time window are learned by NS-Prior-LDA, using the normal states as prior; 3) events are detected by monitoring the change of topical word frequencies; 4) normal states are further maintained by detected events incrementally.
Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
And further experiments on \textit{reddit} also demonstrate that \textsc{NSDetector} can be easily adapted on other cyberspace datasets.
%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well. 
\end{abstract}

@@

\textbf{Event.} We define the event in the given time window \(t\) as the set of tweets denoted by \( \{ \bm{w_{te}}\}\).
The event related tweets in set \( \{ \bm{w_{te}}\}\)  hold two properties: (1) it is different from user \(u\)'s long term interests and (2) it is similar with other tweets in the set.
The task of event detection is to find out all the events in corpus.
Different methods treat the above properties in different ways: LSH based methods\cite{petrovic2010streaming} treat the difference and simliarity in word vector space; while the topic model based methods\cite{timeUserLDA2012finding} take the semantic meaning into consideration.
Under the framework of topic model, we divide the topics into user interest related topics and bursty event related topics, and further promote an online learning model UMIETM.
\subsection{Normal States' Initialization}
\begin{algorithm}
\caption{Normal States' Initialization from Knowledge Base}
\label{alg:normalStatesInit}
\KwIn{Taxonomy's Directed Acyclic Graph \(G^{(0)}\), Category-Page Bipartite Graph \(G^{(1)}\), Page-Content Bipartite Graph \(G^{(2)}\), topic related category node \(c\)}
\KwOut{Normal states \(\bm{f}_c\) on topic \(c\)}
\(Pages(c)\leftarrow \varnothing\)\\
\(SuccessorNodes(c) \leftarrow \) Breadth-first-search(\(G^{(0)},c\))\\
\For{\(node \in SuccessorNodes(c)\)}{
    \(Pages(c) \leftarrow Pages(c) \cup G^{(1)}.neighbours(node)\)\\
}
\(WordFrequencyTable(c) \leftarrow \) do word count on the text contents of \(Pages(c)\) \\
\(WordFrequencyTable(All) \leftarrow \) do word count on the text contents of all pages in \(G^{(2)}\).\\
\For{word \(w\) in WordFrequencyTable(All).keys()}{
    \(\tau_{c,w} \leftarrow \) \(w\)'s chi-square score on \(WordFrequencyTable(c)\) and \(WordFrequencyTable(All)\).
}
\Return{\(\bm{f}_c\)}
\end{algorithm}

\cite{faralli2015large} propose the Twixonomy Graph.

%TODO
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{img/initializationExample.pdf}  
    \caption{Illustration on how to train normal states from wikipedia,( an approximation to the full history information).}
    \label{fig:modelDesc}
\end{figure}

### 2017-03-22 paper/camera_ready/Source_64/DASFAA17_regular_64.tex
camera ready folder done
remove duplicate references

\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}%used for theorem and definition
\usepackage{showframe}%show the margin
%\usepackage{ulem}%used for uwave
\usepackage{comment}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithmic}

@@

\usepackage{hyperref}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection\thanks{This research is supported by the Natural Science Foundation of China (Grant No. 61572043), and the National Key Research and Development Program (Grant No. 2016YFB1000704).}}
\titlerunning{Transfer Learning for Accurate Event Detection\ }
\author{Weijing Huang\inst{1} \and Tengjiao Wang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Yazhou Wang\inst{1} }
\institute{\(^{1}\)Key Laboratory of High Confidence Software Technologies (Ministry of Education), EECS, Peking University, Beijing, China \\ 
\path{huangwaleking@gmail.com,{tjwang,pekingchenwei}@pku.edu.cn}\\ 
\path{pkuwangyz@gmail.com}
}

\maketitle
% BEGIN
% To Proceeding Editors:
% Special codes there for remove page numbers in the LaTeX documents
\thispagestyle{empty}
\pagestyle{empty}
%
% END

@@

\textbf{Knowledge Base.} Many general knowledge bases and customized knowledge bases are constructed and utilized for different text mining tasks. 
For example, Probase\cite{wu2012probase} constructs a large general probabilistic \textit{IsA} taxomomy from webpages, and is used for semantic web search, and text classification\cite{wang2014concept}.
Such kind efforts are also made by DBPedia\cite{auer2007dbpedia}, Yago\cite{fabian2007yago}, and Freebase\cite{bollacker2008freebase}. 
These works manages knowledge as tuples on graph. 
However the query on large graph is very expensive\cite{huang2011scalable}, which is not very suitable for the scene of quickly and accurately detecting events.
The customized knowledge bases such as EVIN\cite{kuzey2014evin}, Event Registry\cite{leban2014eventRegistry}, and Story-base\cite{wu2015storybase}, are designed for managing events.
These knowledge bases are mainly built on news articles.
EVIN maps the existing event-related news articles into semantic classes. 
Event Registry collects the articles by the API of News Feed Service\cite{trampuvs2012newsfeed}, then detects events, and provides the structural information of the events, such as the related Wikipedia article, timestamp, and location etc. 
Storybase introduces Wikipedia current events\footnote{\url{https://en.wikipedia.org/wiki/Portal:Current_events}} as the resources for constructing event-and-storyline knowledge base on news articles, which are provided by GDELT project\cite{leetaru2013gdelt}.
As the news articles may lag behind the microblogs when the emergency of events, it's not enough to detect events from microblog stream by directly applying these customized knowledge bases.

\textbf{Transfer Learning.} 
%Transfer learning uses the knowledge in the source domain to enhance the performance of learning tasks on the target domain. \cite{dai2007transferring}
Although the training examples in the target domain is very sparse, transfer learning\cite{Pan2010A} can utilize the domain-independent knowledge as the bridge to fill the information gap between source domain and target domain\cite{Xiang2010Bridging} to get more ``examples" for training.
By bayesian transfer learning, \cite{dai2007transferring} uses the distribution in source domain as the prior knowledge for text classfication.
And inspired by this idea, we propose the \textit{category-level topic} as the bridge for transferring knowledge.

>>>>

\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}%used for theorem and definition
%\usepackage{showframe}%show the margin
%\usepackage{ulem}%used for uwave
\usepackage{comment}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithmic}

@@

\usepackage{hyperref}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection\thanks{This research is supported by the Natural Science Foundation of China (Grant No. 61572043), and the National Key Research and Development Program (Grant No. 2016YFB1000704).}}
\titlerunning{Category-Level Transfer Learning from Knowledge Base to Microblog Stream\ }
\author{Weijing Huang\inst{1} \and Tengjiao Wang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Yazhou Wang\inst{1} }
\institute{\(^{1}\)Key Laboratory of High Confidence Software Technologies (Ministry of Education), EECS, Peking University, Beijing, China \\ 
\path{huangwaleking@gmail.com,{tjwang,pekingchenwei}@pku.edu.cn}\\ 
\path{pkuwangyz@gmail.com}
}

\maketitle
% BEGIN
% To Proceeding Editors:
% Special codes there for remove page numbers in the LaTeX documents
%\thispagestyle{empty}
%\pagestyle{empty}
%
% END

@@

\textbf{Knowledge Base.} Many general knowledge bases and customized knowledge bases are constructed and utilized for different text mining tasks. 
For example, Probase\cite{wu2012probase} constructs a large general probabilistic \textit{IsA} taxomomy from webpages, and is used for semantic web search, and text classification\cite{wang2014concept}.
Such kind efforts are also made by DBPedia\cite{auer2007dbpedia}, Yago\cite{suchanek2007yago}, and Freebase\cite{bollacker2008freebase}. 
These works manages knowledge as tuples on graph. 
However the query on large graph is very expensive\cite{huang2011scalable}, which is not very suitable for the scene of quickly and accurately detecting events.
The customized knowledge bases such as EVIN\cite{kuzey2014evin}, Event Registry\cite{leban2014eventRegistry}, and Story-base\cite{wu2015storybase}, are designed for managing events.
These knowledge bases are mainly built on news articles.
EVIN maps the existing event-related news articles into semantic classes. 
Event Registry collects the articles by the API of News Feed Service\cite{trampuvs2012newsfeed}, then detects events, and provides the structural information of the events, such as the related Wikipedia article, timestamp, and location etc. 
Storybase introduces Wikipedia current events\footnote{\url{https://en.wikipedia.org/wiki/Portal:Current_events}} as the resources for constructing event-and-storyline knowledge base on news articles, which are provided by GDELT project\cite{leetaru2013gdelt}.
As the news articles may lag behind the microblogs when the emergency of events, it's not enough to detect events from microblog stream by directly applying these customized knowledge bases.

\textbf{Transfer Learning.} 
%Transfer learning uses the knowledge in the source domain to enhance the performance of learning tasks on the target domain. \cite{dai2007transferring}
Although the training examples in the target domain is very sparse, transfer learning\cite{pan2010survey} can utilize the domain-independent knowledge as the bridge to fill the information gap between source domain and target domain\cite{Xiang2010Bridging} to get more ``examples" for training.
By bayesian transfer learning, \cite{dai2007transferring} uses the distribution in source domain as the prior knowledge for text classfication.
And inspired by this idea, we propose the \textit{category-level topic} as the bridge for transferring knowledge.
